---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices are part of the “quantified self” movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks.

## Loading and preprocessing the data
Load the activity data and explore it.

```{r }
Activity <- read.csv ("~/Desktop/RepData_PeerAssessment1/Activity.csv")
head(Activity)
str(Activity)
```
#### Ploting the Histogram of the steps
Plotting the histogram of the daily steps using the base plot system.
```{r }
daily <- aggregate(steps ~ date, data = Activity, sum, na.rm = TRUE)
hist(daily$steps,breaks = 15, main = "The Histogram of Daily Steps", xlab = "Number of steps", col = "red")
```

## What is mean total number of steps taken per day?
The mean and the median of the daily data aggregated earlier is calculated and printed.
```{r }
Mean <- mean(daily$steps)
print(paste("The mean of daily activity is", round(Mean, 3)))

Median <- median(daily$steps)
print(paste("The median of daily activity is", Median))
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
